\textbf{SPECFEM3D}\\ \textbf{Cartesian}\\ \textbf{User Manual}

### 2023-11-14 doc/USER_MANUAL/02_getting_started.tex
updates version number to 4.1.0

>>>>

%-----------------------------------------------------------------------------------------------------------------------------------%
\section{Using HDF5 for file I/O}
%-----------------------------------------------------------------------------------------------------------------------------------%

As file I/O can be a bottleneck in large-scale simulations, SPECFEM3D supports file I/O using the HDF5 format
for movie snapshots and database files. To support this feature, you will need to compile the code with corresponding HDF5 flags.
The configuration of the package could look for example like:
{\small
\begin{verbatim}
  ./configure --with-hdf5 HDF5_INC="/opt/homebrew/include" HDF5_LIBS="-L/opt/homebrew/lib" \
      ..
\end{verbatim}
}
In the main \texttt{Par\_file}, you will then have to turn on the HDF5 flag \texttt{HDF5\_ENABLED}.
Note that additional MPI processes can be launched specifically to handle the file I/O in an asynchronous way.
The number of these additional MPI processes is specified by the parameter \texttt{HDF5\_IO\_NODES}, such that
the total number of MPI processes to launch the executables becomes \texttt{NPROC + HDF5\_IO\_NODES}.

### 2023-11-14 doc/USER_MANUAL/authors.tex
updates version number to 4.1.0

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team: in alphabetical order,
Michael Afanasiev,
Rafael Almada,
Jean-Paul (Pablo) Ampuero,
\'Etienne Bachmann,
Kangchen Bai,
Piero Basini,
Stephen Beller,
Jordan Bishop,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Cl\'ement Durochat,
Percy Galvez,
Rene Gassmoeller,
Hom Nath Gharti,
Dominik G\"oddeke,
Leopold Grinberg,
Aakash Gupta,
Vala Hj\"orleifsd\'ottir,
Foivos Karakostas,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Youshan Liu,
David Luet,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Geordie McBain,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Ryan Modrak,
Vadim Monteiller,
Surendra Nadh Somala,
Masaru Nagaso,
Tarje Nissen-Meyer,
Elif Oral,
Daniel Peter,
Kevin Pouget,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
James Smith,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Eduardo Valero Cano,
Brice Videau,
Jean-Pierre Vilotte,
Huihui Weng,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\newline

>>>>

%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
%%%%%%%% please do NOT merge the lines of the paragraph below, it makes it difficult to insert new names in alphabetical order; leave a single name per line
Since then it has been developed and maintained by a development team: in alphabetical order,
Michael Afanasiev,
Rafael Almada,
Jean-Paul (Pablo) Ampuero,
\'Etienne Bachmann,
Kangchen Bai,
Piero Basini,
Stephen Beller,
Jordan Bishop,
C\'eline Blitz,
Alexis Bottero,
Ebru Bozda\u{g},
Emanuele Casarotti,
Joseph Charles,
Min Chen,
Paul Cristini,
Cl\'ement Durochat,
Percy Galvez,
Rahul Garg,
Rene Gassmoeller,
Hom Nath Gharti,
Dominik G\"oddeke,
Leopold Grinberg,
Aakash Gupta,
Vala Hj\"orleifsd\'ottir,
Foivos Karakostas,
Sue Kientz,
Dimitri Komatitsch,
Jes\'us Labarta,
Nicolas Le Goff,
Pieyre Le Loher,
Matthieu Lefebvre,
Qinya Liu,
Youshan Liu,
David Luet,
Yang Luo,
Alessia Maggi,
Federica Magnoni,
Roland Martin,
Ren\'e Matzen,
Geordie McBain,
Dennis McRitchie,
Matthias Meschede,
Peter Messmer,
David Mich\'ea,
Ryan Modrak,
Vadim Monteiller,
Surendra Nadh Somala,
Masaru Nagaso,
Tarje Nissen-Meyer,
Elif Oral,
Daniel Peter,
Kevin Pouget,
Max Rietmann,
Elliott Sales de Andrade,
Brian Savage,
Bernhard Schuberth,
Anne Sieminski,
James Smith,
Leif Strand,
Carl Tape,
Jeroen Tromp,
Eduardo Valero Cano,
Brice Videau,
Jean-Pierre Vilotte,
Huihui Weng,
Zhinan Xie,
Chang-Hua Zhang,
Hejun Zhu.\newline
